%-------------------------
% Resume in Latex
% Author : Anirban Bala Pranto
% Website: https://github.com/anirbanpranto/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{http://anirbanpranto.me/}{\Large Anirban Bala Pranto}} & Email : \href{mailto:anirbanpranto@gmail.com}{anirbanpranto@gmail.com}\\
  \href{http://anirbanpranto.me/}{http://www.anirbanpranto.me} & Mobile : +60-18-971-7552 \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Multimedia University}{Cyberjaya, Malaysia}
      {Bachelor of Computer Science (Honours);  CGPA: 3.97}{Mar. 2021 - Dec. 2023}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Auronex Sdn Bhd}{Kuala Lumpur, Malaysia}
      {Software Engineer (Part Time)}{Mar. 2021 - Present}
      \resumeItemListStart
        \resumeItem{Subscription Model}
          {Implemented and designed a membership subscription model for \textbf{\href{https://parceldaily.com}{Parcel Daily}} which allows users to get special pricing and automatic billing every month. }
        \resumeItem{Invoice Generator}
          {Implemented and designed an invoice generator RESTful API for \textbf{\href{https://parceldaily.com}{Parcel Daily}} which allows users to get their monthly invoice and their total spending for that month.}
         \resumeItem{Quote API}
          {Implemented price quote RESTful API for \textbf{\href{https://parceldaily.com}{Parcel Daily}} which is being used by unique 40,000+ users monthly.}
         \resumeItem{Tracking API}
          {Implemented tracking for \textbf{J\&T, Poslaju \& DHL} in \textbf{\href{https://parceldaily.com}{Parcel Daily}} that allows users to view the status of their delivery and history.}
         \resumeItem{Courier Integration}
          {Integrated \textbf{J\&T, Poslaju \& DHL} courier services in \textbf{\href{https://parceldaily.com}{Parcel Daily}} that allows users to place orders from these courier services through Parcel Daily platform.}
         \resumeItem{Consignment Note Generator}
          {Implemented a service to generate consignment notes for different courier services in \textbf{\href{https://parceldaily.com}{Parcel Daily}} in a standardized form and upload them to the cloud (AWS S3) and a REST API endpoint to download the consignment notes in either Thermal or A4 format.}
         \resumeItem{Page Loading Optimization}
          {Implemented a order fetching API in \textbf{\href{https://parceldaily.com}{Parcel Daily}} which prefetches number of pages and creates blank pages, data is only fetched when user clicks the page. This reduced the page load time from 15 seconds to less than 1.5 seconds. (10x Performance increase)}
      \resumeItemListEnd
    
    \resumeSubheading
      {Auronex Sdn Bhd}{Kuala Lumpur, Malaysia}
      {Software Engineer Intern}{Nov. 2020 - Mar. 2021}
      \resumeItemListStart
        \resumeItem{OTP}
          {Developed an OTP microservice for an ad campaign for P\&G, the feature was deployed, and used all over Malaysia and Singapore in Christmas 2020.}
        \resumeItem{Video Upload Pipeline}
          {Implemented a video upload pipeline using MUX and NodeJS. Reduced the backend service memory usage by 80\% with the use of upload tokens that enabled the users to upload from the client side.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{\href{https://github.com/anirbanpranto/CyberRent}{Cyber Rent}}
      {A room renting service desktop app that built as part of Object Oriented Analysis and Design class at Multimedia University. This application demonstrates the use of OO Design Patterns in real life.}
    \resumeSubItem{\href{https://github.com/anirbanpranto/Crab}{Crab}}
      {Grab, but for cash washers. It's an app built as part of Software Engineering Fundamentals class in Multimedia University. It allows users to book and washers to accept car washing gigs, and track their job history and receive payments.}
  \resumeSubHeadingListEnd

\section{Leadership Experiences}
    \resumeSubHeadingListStart
        \resumeSubheading
          {IT Society}{Cyberjaya, Malaysia}
          {Vice President External}{Jan. 2021 - Jan. 2022}
          \resumeItemListStart
            \resumeItem{CodeNection 2021}
              {Managed and lead a team of 25 students and directed a national programming competition in Malaysia. The competition had over 70 teams participating and gained industry sponsorships from MNCs.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd


%
%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
 \resumeSubHeadingListStart
   \item{
        \textbf{Languages}{: Javascript/Typescript, Python, Java, SQL}
   }
   \item{
        \textbf{Technologies}{: AWS EC2, AWS S3, MongoDB, React, Vue, Google Compute Engine, Nginx, Cloudflare, Redis}
   }
 \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}